---
title: ""
format: 
  html:
    css: assets/style.css
    template: assets/template.html
bibliography: manuscript/references.bib
csl: manuscript/apa.csl
link-citations: true
editor: 
  markdown: 
    wrap: sentence
---


```{r}
#| include: false
#| echo: false
#| 
library(tidyverse)
library(gert)
library(glue)
#source('scripts/dependencies.R')
knitr::opts_chunk$set(echo = F, message = F, warning = F)

```
<br>

This repository contains data, code, and output for a manuscript with the working title "Attention shifting and inhibition abilities among people from adverse conditions". 

Do you want to download or clone the materials for this project? Go to [https://github.com/stefanvermeent/liss_ef_2024](https://github.com/stefanvermeent/liss_ef_2024)

## Directory Structure {#structure}

The names of each folder are intended to be self-explanatory.
There are eight top-level folders to organize the inputs and outputs of this project:

1.  [`Preregistration`](https://stefanvermeent.github.io/liss_ef_2024/preregistration/README.html): The preregistration for the main analyses.
3.  [`Manuscript`](https://stefanvermeent.github.io/liss_ef_2024/manuscript/README.html): The manuscript written in Quarto.
4.  [`Supplement`](https://stefanvermeent.github.io/liss_ef_2024/supplement/README.html): a supplemental text (to be submitted with the manuscript) documenting all secondary analyses in detail.
5.  [`Scripts`](https://stefanvermeent.github.io/liss_ef_2024/scripts/README.html): R-scripts that read, analyze, and produce all analysis objects.
6.  [`Data`](https://stefanvermeent.github.io/abcd_ddm/data/README.html): Folder in which real LISS data can be placed to make the analyses fully reproducible. Note that we cannot openly share the raw data on the open repository. 
7.  [`Analysis Objects`](https://stefanvermeent.github.io/liss_ef_2024/analysis_objects/README.html): Folder containing all analysis objects.
8.  [`Codebooks`](https://stefanvermeent.github.io/liss_ef_2024/codebooks/README.html): lists of variable names, labels, and value labels (where applicable).

Click on each of the folders to get more details.

## Overview of project milestones

Below is an overview of all the project milestones, such as first-time data access, submissions, and revisions.
Data access events were automatically captured using custom code, which over the course of this project was collected in the R package `projectlog` [https://stefanvermeent.github.io/projectlog/](https://stefanvermeent.github.io/projectlog/).


```{r}
#| results: 'asis'
#| echo: false

x <- gert::git_log(max = 10000) |> 
  select(commit, author, time, message) |>
  # Some custom coding because we switched to using the projectlog package for the final data_access event
  mutate(message = ifelse(str_detect(message, "first-time access to ivs"), str_c("[[data_access]] ", message), message)) |> 
  mutate(message = ifelse(str_detect(message, "Submission of Stage 2 manuscript"), str_c("[[submission]] ", message), message)) |>
  mutate(message = ifelse(str_detect(message, "Stage 2 accepted manuscript at Developmental Science"), str_c("[[accepted]] ", message), message)) |>
  (function(.) filter(., str_detect(string = .$message, pattern = "^\\[\\[")))() |> 
  separate(message, into = c("message", "data_hash", 'code'), sep = "\n") |> 
  separate(message, into = c("milestone", "description"), sep = "\\]\\]\\s") %>% 
  distinct(data_hash, description, .keep_all = TRUE) %>%
  mutate(
    milestone = map_chr(milestone, function(milestone) {
      milestone |> 
        str_remove("\\[\\[") |>
        str_replace("_", " ") |> 
        str_to_title()
    }),
    data_hash = str_remove(data_hash, "^object_hash ")
  ) |> 
  select(time, commit, milestone, description, code, data_hash) |> 
  mutate(
    code = str_replace_all(code, "\\|\\>", "\\|\\>\\\n"),
    link_to_git = paste0(
       gert::git_remote_list()$url |> str_remove(string = _, pattern = "\\.git$"), "/tree/", commit)
    ) |>
  arrange(desc(time)) |> 
  glue_data("  - **[{time}]({link_to_git}): {description}**
        - **Milestone:** {milestone}
        - **Data MD5 hash**: {data_hash}
        - [Link to code snippet](https\\://github.com/StefanVermeent/abcd_ddm/blob/main/.projectlog/{commit}.R)
        \n
    ")
x

```


### Contact

For questions or comments, feel free to contact me at p.c.s.vermeent@gmail.com.
